Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-06 writeup/conStruct.tex
fixed wording for new cols

A second caveat is that, in some instances, 
membership in the same cluster may not mean that samples are particularly related.
If covariance within a cluster decays sharply with distance, 
and the cluster-specific relatedness parameter $\phi^{(k)}$ is low, 
individuals at a far spatial remove may be in the same cluster but have very low pairwise relatedness.
It is possible that this is happening in Fig \ref{populus_sp_pies}\subref{populus_sp_pies:K3}. 
At $K=3$, the southernmost populations of \textit{P. trichocarpa} are in the green cluster, 
whose other neighbors are to the north, with an intervening group of populations in the red cluster, 
and at $K=4$, those southernmost samples split out and become their own yellow cluster.
Again, we encourage users to run analyses across multiple values of $K$, 
and to examine the spatial covariance functions within layers when interpreting results.

>>>>

A second caveat is that, in some instances, 
membership in the same cluster may not mean that samples are particularly related.
If covariance within a cluster decays sharply with distance, 
and the cluster-specific relatedness parameter $\phi^{(k)}$ is low, 
individuals at a far spatial remove may be in the same cluster but have very low pairwise relatedness.
It is possible that this is happening in Fig \ref{populus_sp_pies}\subref{populus_sp_pies:K3}. 
At $K=3$, the southernmost populations of \textit{P. trichocarpa} are in the yellow cluster, 
whose other neighbors are to the north, with an intervening group of populations in the red cluster, 
and at $K=5$, those southernmost samples split out and become their own cluster.
Again, we encourage users to run analyses across multiple values of $K$, 
and to examine the spatial covariance functions within layers when interpreting results.
